Responses to the Reviewers' Comments

### 2024-10-11 Response/Paper_Res.tex
Rev_V6

\setcounter{section}{0}
\renewcommand*{\thesection}{\Roman{section}}
\makeatletter

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{itemize}
\item a) We have included the literature review in Section II of the revised manuscript and provided a survey of the recently published state-of-the-art works.
\item b) Furthemore, we have expanded the explanations about each related work and discussed their pros/vons.
\end{itemize}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

@@

Second, we have extended the performance evaluation by comparing the performance of our proposed algorithm with vanilla DQN and DDQN to further specify the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section V of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing capabilities of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods. ..... (COMPLETE IT).

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chart01}
\end{figure}

@@

We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig. 7 and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and D3QN-based computation offloading methods, measured by the average QoE across episodes. As shown in Fig. 7, the average QoE for all computation offloading algorithms rises consistently as the episodes progress, until reaching convergence. Specifically, the vanilla DQN, D3QN, and our proposed algorithm converge after approximately 650, 550, and 400 iterations, respectively. This demonstrates the relatively faster convergence of the QECO algorithm, which also achieves a higher average QoE than the other methods. These results highlight the positive impact of workload prediction by the LSTM network and its advantage in efficiently utilizing the processing capabilities of MDs and ENs.
}}
\end{my}

@@

\vspace{7mm}

@@

\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\caption{\textcolor{blue}{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart1}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart2}
\end{figure}\vspace{-12mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart3}
\end{figure} \vspace{-12mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_2} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart4}
\end{figure}

@@

@@

	We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart01} and Fig.~\ref{chart02}. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart01}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig. 6 (a) shows the average QoE for different values of the task arrival rate. This figure highlights the superiority of the QECO algorithm in providing MDs with an enhanced experience. At lower task arrival rates (i.e., 50-150), QECO performs optimally and maintains an average QoE of at least 0.72, while the other methods experience a steeper decline, with average QoE dropping to 0--0.54. Specifically, at a task arrival rate of 200, QECO improves the average QoE by 91.7\% compared to DCDRL in the positive average QoE range. As task arrival rates increase to 300, the average QoE significantly decreases for all methods due to increased competition for resources in the MEC system. However, QECO still maintains a positive average QoE, while other methods fall to negative values, with a decline of up to -0.17. For higher task arrival rates (i.e., 350–450), QECO experiences a negative average QoE, but it shows at least a 42.6\% and 24.6\% smaller reduction in average QoE compared to RD and DCDRL, respectively. \vspace{3mm}

Fig. 6 (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases from 30 to 110, QECO consistently maintains at least a 29.8\% higher QoE compared to the other methods. Specifically, at a moderate number of 70 MDs, QECO achieves an average QoE of 0.57, showing a 60.3\% improvement compared to DCDRL. It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs. \vspace{3mm}\\\dots }}

@@

				Simulation results with 50 mobile devices and 5 edge nodes validate that the QECO algorithm is able to efficiently recognize the mobile devices' demands and exploit the computational resources of edge nodes. 
				Consequently, it increases the number of completed tasks by 12.2\%, while simultaneously reducing task delay and energy consumption by 11.7\% and 10.8\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of at least 34.8\% compared to \cite{qiu2020distributed}.
}

@@

	In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.

@@

	To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	\dots
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay.

@@

	Some studies explored task offloading problems in more advanced scenarios. Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
	To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.

@@

	To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
	To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
\dots
	To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

@@

	Due to the limited processing capacities of ENs, the processing capacity that an EN allocates to an MD depends on the EN's workload each time. \dots
	To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.

@@

				We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart01} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart01}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

			We consider a MEC environment with 50 MDs and 5 ENs \dots The algorithm's source code is available at \cite{QECO}.

@@

\vfill

>>>>

\setcounter{section}{0}
\renewcommand*{\thesection}{\Roman{section}}
\makeatletter
\setcounter{table}{0}

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{itemize}
\item a) We have included the literature review in Section II of the revised manuscript and provided a survey of the recently published state-of-the-art works.
\item b) Furthemore, we have expanded the explanations about each related work and discussed their pros/vons.
\end{itemize}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table111} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table111}}
\end{table*}

@@

Second, we have extended the performance evaluation by comparing the performance of our proposed algorithm with vanilla DQN and DDQN \cite{van2016deep} to further specify the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section V of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing capabilities of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods.

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chart000}
\end{figure}

@@

	\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart000} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart000}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs.
}}
\end{my}

@@

@@

\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ drop_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	\caption{\textcolor{blue}{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart1}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart2}
\end{figure}\vspace{-8mm}
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart3}
\end{figure} 
\begin{figure}[H]\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_2} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.33\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}

	\caption{\textcolor{blue}{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}}
	\label{chart44}
\end{figure}

@@

\begin{figure}[H]
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.6\linewidth]{m1}
	\vspace*{-3mm}
	\caption{\textcolor{blue}{The convergence of the average QoE across episodes under different DQN-based methods.}}
	\vspace*{-3mm}
	\label{chart111}
\end{figure}
		\begin{my}{1cm}{1cm}
	\rev{
		{\

@@

\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart111} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart111}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

\,\,\,\,We further investigate the overall improvement achieved by the QECO algorithm in comparison to other methods in terms of the average QoE. This metric signifies the advantages MDs obtain by utilizing different algorithms. Fig.~\ref{chart44} (a) shows the average QoE for different values of the task arrival rate. This figure highlights the superiority of the QECO algorithm in providing MDs with an enhanced experience. At lower task arrival rates (i.e., 50-150), QECO performs optimally and maintains an average QoE of at least 0.72, while the other methods experience a steeper decline, with average QoE dropping to 0--0.54. Specifically, at a task arrival rate of 200, QECO improves the average QoE by 91.7\% compared to DCDRL in the positive average QoE range. As task arrival rates increase to 300, the average QoE significantly decreases for all methods due to increased competition for resources in the MEC system. However, QECO still maintains a positive average QoE, while other methods fall to negative values, with a decline of up to -0.17. For higher task arrival rates (i.e., 350–450), QECO experiences a negative average QoE, but it shows at least a 42.6\% and 24.6\% smaller reduction in average QoE compared to RD and DCDRL, respectively. \vspace{3mm}

\,\,\,\,Fig.~\ref{chart44} (b) illustrates the average QoE when we increase the number of MDs. The EN's workload grows when there are a larger number of MDs, leading to a reduction in the average QoE of all methods except LC. However, QECO effectively manages the uncertain load at the ENs. When the number of MDs increases from 30 to 110, QECO consistently maintains at least a 29.8\% higher QoE compared to the other methods. Specifically, at a moderate number of 70 MDs, QECO achieves an average QoE of 0.57, showing a 60.3\% improvement compared to DCDRL. It is worth noting that although improvements in each of the QoE factors can contribute to enhancing system performance, it is essential to consider the user's demands in each time slot. Therefore, the key difference between QECO and other methods is that it prioritizes users' demands, enabling it to strike an appropriate balance among them, ultimately leading to a higher QoE for MDs. \vspace{3mm}\\\dots }}

@@

				Simulation results with 50 mobile devices and 5 edge nodes validate that the QECO algorithm is able to efficiently recognize the mobile devices' demands and exploit the computational resources of edge nodes. 
				Consequently, it increases the number of completed tasks by 12.2\%, while simultaneously reducing task delay and energy consumption by 11.7\% and 10.8\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of at least 34.8\% compared to an existing algorithm.
}

@@

	\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.

@@

	\,\,\,\,To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	\dots
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay.

@@

	\,\,\,\,Some studies explored task offloading problems in more advanced scenarios. Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
	To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent deep Q-network (DQN)-based algorithm.

@@

	\,\,\,\,To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
	To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
\dots
	\,\,\,\,To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

@@

	\,\,\,\,Due to the limited processing capacities of ENs, the processing capacity that an EN allocates to an MD depends on the EN's workload each time. \dots
	To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments.

@@

				\,\,\,\,We finally delve into the investigation of the convergence performance of the QECO algorithm in Fig.~\ref{chart01} and Fig. 8. To validate the effectiveness of the QECO algorithm, we assess its convergence rate compared to the vanilla DQN and DDQN configurations \cite{van2016deep}, measured by the average QoE across episodes. As shown in Fig.~\ref{chart01}, as the episodes progress, the MD's network learns efficient policies, ultimately stabilizing as it approaches convergence. Specifically, the DQN, DDQN, and our proposed QECO algorithm converge after approximately 650, 550, and 450 iterations, respectively. The QECO algorithm demonstrates the faster convergence while achieves a higher average QoE than the other methods. underscore the beneficial impact of workload prediction by the LSTM network and highlight its effectiveness in efficiently utilizing the processing capabilities of  MDs and ENs. \\\dots }}

@@

			\,\,\,\,We consider a MEC environment with 50 MDs and 5 ENs \dots The algorithm's source code is available at \cite{QECO}.

@@
